---
title: "Weight of Fish"
author: "Andrew Valles Tovar"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file="Fish.csv", header = TRUE)
```


## Perch
```{r}
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


### Best Two regressor model
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
The best model and the best two regressor model from the chart above is Height and Width. The adjusted R squared for this model is the highest out of the others at 0.94 R-squared. 

## Five Element Perch Model
```{r}
best.Perch_model <- lm(Weight~Height+Width,data=Perch)
five_element_perch_model <- lm(Weight~.,data=Perch)
anova(best.Perch_model, five_element_perch_model)
```
According to the statistics, there is no significant difference between the two models. The P-value is almost 1, meaning they're not that different.

## Pike
```{r}
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -(Species))
```
### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
best.model <- lm(Weight~Length1+Length3,data=Pike)
summary(best.model)
```
The best two regressor model from the chart above is Length1 and Length3. It is not the best model in this case as the model's adjusted R-squared is 0.9649, which is lower than the other models so it is the fourth best model.

## Five Element Pike Model
```{r}
best.Pike_model <- lm(Weight~Length1+Length3,data=Pike)
five_element_pike_model <- lm(Weight~.,data=Pike)
anova(best.Pike_model, five_element_pike_model)
```
The five element model is our best model based on these statistics. It is significant below the .05 level.

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements