---
title: "Weight of Fish"
author: "Andrew Valles Tovar"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file="Fish.csv", header = TRUE)
```


## Perch
```{r}
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -(Species))
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


### Best Two regressor model
```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```
The best model and the best two regressor model from the chart above is Height and Width. The adjusted R squared for this model is the highest out of the others at 0.94 R-squared. 

## Five Element Perch Model
```{r}
best.Perch_model <- lm(Weight~Height+Width,data=Perch)
five_element_perch_model <- lm(Weight~.,data=Perch)
anova(best.Perch_model, five_element_perch_model)
```
According to the statistics, there is no significant difference between the two models. The P-value is almost 1 and the residual sum of squares is slightly below the two model, meaning they're not that different.

## Pike
```{r}
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -(Species))
```
### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
best.model <- lm(Weight~Length1+Length3,data=Pike)
summary(best.model)
```
The best two regressor model from the chart above is Length1 and Length3. It is not the best model in this case as the model's adjusted R-squared is 0.9649, which is lower than the other models so it is the fourth best model.

## Five Element Pike Model
```{r}
best.Pike_model <- lm(Weight~Length1+Length3,data=Pike)
five_element_pike_model <- lm(Weight~.,data=Pike)
anova(best.Pike_model, five_element_pike_model)
```
The five element model is our best model based on these statistics. The residual sum of squares for the five element model is extraordinarily higher than the two element model. It is significant below the .05 level.

## Roach
```{r}
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -(Species))
```
### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```
### Best Two regressor model
```{r}
best.model <- lm(Weight~Length3+Width,data=Roach)
summary(best.model)
```
According to the graph and data, the best model and the best two regressor model is Length3 and Width. The adjusted R squared for this model is the highest out of the others at 0.8482 R-squared. 

## Five Element Roach Model
```{r}
best.Roach_model <- lm(Weight~Length3+Width,data=Roach)
five_element_roach_model <- lm(Weight~.,data=Roach)
anova(best.Roach_model, five_element_roach_model)
```
For this data, we are comparing the two element model and the five element model. The P-value is 0.9 and the R-sum of squares for the five element model is slightly below than the two element model. In conclusion, there is hardly any difference between the models with the two element model being better.

## Final Summary Statements
